---
title: "cohousing comps"
output:
    bookdown::html_document2:
      highlight: zenburn
      toc: true
      toc_float: true
      code_folding: hide
      number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(magrittr)
library(ggrepel)
## Sets defaults for R chunks
knitr::opts_chunk$set(echo = TRUE, # echo = TRUE means that code will show
                      cache = FALSE,
                      #cache = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      fig.show="hold",
                      fig.pos= "htbp",
                      fig.path = "figs/",
                      fig.align='center',
                      fig.cap = '   ',
                      fig.retina = 3,
                      fig.height = 7,
                      fig.width = 6,
                      out.width = "100%",
                      out.extra = "")

theme_set(theme_minimal())
theme_update(plot.title = element_text(hjust=0.5,size=12))

# defaults for plots
library(ggplot2); theme_set(theme_minimal());
options(
  ggplot2.continuous.color = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_color_discrete <- function(...){
  scale_color_viridis_d(..., direction = -1,
                        begin = 0, end = .6, option = "plasma")}
scale_fill_discrete <- function(...){
  scale_fill_viridis_d(..., direction = -1,
                       begin = 0, end = .6, option = "plasma")}

scale_color_continuous <- function(...){
  scale_color_viridis_c(..., direction = -1,
                        option = "plasma")}
scale_fill_continuous <- function(...){
  scale_fill_viridis_c(..., direction = -1,
                       option = "plasma")}


# Table formatting
replace_q <- function(x){
  x |> replace_na("?")
}

# Table formatting
library(kableExtra)
kablebox <- .  %>% 
  mutate_all(as.character) %>%
  mutate_all(replace_q) %>%
  slice_head(n = 100) %>%
  knitr::kable() %>%
  kable_styling() %>%
  scroll_box(height = "400px")
```

I'm compiling comps data in [this google sheet](https://docs.google.com/spreadsheets/d/1p9XG_h6bDkcHINCmrU-MX_cS5295tX7acTKX56SOM-A/edit#gid=0) from [these pdfs](https://drive.google.com/drive/folders/1ps376ofdR6IMLjpdOWsQEJ_nAg7zeAAs).

```{r eval=F, include=FALSE}
library(googledrive)
library(googlesheets4)
drive_auth(email = "devin.jl@gmail.com")

d <- drive_get("https://docs.google.com/spreadsheets/d/1p9XG_h6bDkcHINCmrU-MX_cS5295tX7acTKX56SOM-A/edit#gid=0") %>% read_sheet()

d <- d |> mutate(level = replace_na(level, "?") %>% 
                   str_replace("both", "both (townhouse)"))


write_csv(d, file = "data/comps.csv")
```

> Note: Instead of recording the number of bedrooms (the typical measure of space), I'm recording whether these units include the upper level, lower level, or both. This is because pretty much all of the upper-level apartments are the same size, the lower-level units are the same size, and the full townhouse units are the roughly the same size (though they might have been carved up into different numbers of bedrooms). For example, the Touchstone unit #26 that we are looking at has 2 small bedrooms on the main floor (it is a lower-level unit), whereas many others just have one large bedroom on the main (lower) level.

```{r comps-by-bath-and-level}
d <- read_csv("data/comps.csv")

d |> kablebox()



d |>
  distinct(unit, year, sold, level, bath) |>
  drop_na(year) |>
  ggplot() + 
  aes(label = unit,
      x = year,
      #y = `net value`,
      y = sold,
      color = level) +
  #geom_smooth(method = "lm", se = FALSE) +
    geom_point(alpha = .5, size = 7) +
  geom_point(alpha = .7, aes(size = bath), color = "black", fill = NA, shape = 1) +
  geom_text_repel(force_pull	= .1, nudge_x	=.3) +
  labs(title = "Comps for Touchstone #26",
       caption = "t = Touchstone, g = Great Oak, s = Sunward",
       y = "Price (Thousands)",
       x = "",
       size = "Baths", 
       color = "Level") + 
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.text.x = element_blank()) + 
    scale_y_continuous(labels=scales::dollar_format(), breaks =  seq(0, 500, 20)) +  facet_wrap("year", nrow = 1, scales = "free_x")



d |>
  distinct(unit, year, sold, level, bath, `sq ft`) |>
  drop_na(year) |>
  ggplot() + 
  aes(label = unit,
      x = `sq ft`,
      #y = `net value`,
      y = sold,
      color = level) +
  #geom_smooth(method = "lm", se = FALSE) +
    geom_point(alpha = .5, size = 7) +
  geom_point(alpha = .7, aes(size = bath), color = "black", fill = NA, shape = 1) +
  geom_text_repel(force_pull	= .1, nudge_x	=.3) +
  labs(title = "Comps for Touchstone #26",
       caption = "t = Touchstone, g = Great Oak, s = Sunward",
       y = "Price (Thousands)",
       x = "sq ft",
       size = "Baths", 
       color = "") + 
    scale_y_continuous(labels=scales::dollar_format(), breaks =  seq(0, 500, 20)) 
```

# Linear regression estimates

```{r, predicted-price, fig.width=7, fig.height=3}
d$price <- d$`net value`

m <- lm(price ~ level + year,
        data = d)

m1 <- lm(price ~ level + year +`sq ft`,
        data = d)

m2 <- lm(price ~ level + year +`sq ft` + bath,
        data = d)


tibble(
  unit = d$unit,
  estimate = predict(m) |> round() |> paste("Thousand")
) |> 
  kablebox()


library(marginaleffects)

t26 = d |> filter(unit == "t26") 

library(purrr)

# function to extract estimates for Touchstone 26
pred <- function(m){
  predictions(m, t26, conf_level = .2) |> 
    tidy() |>
    mutate(model = m$call[2] |> as.character())
}


# for base model 
p <- predictions(m, t26) 

# for all models 
models <- list(m, m1, m2) 

p <- map_df(models, pred)

p <- p |> select(estimate, conf.low, conf.high, model) |> mutate_if(is.numeric, round)

p |> kablebox()

p |> 
  ggplot() + 
  aes(y = estimate, x = model) + 
  geom_pointrange(aes(ymin = conf.low,
                  ymax = conf.high), 
                  alpha = .7,
                  position = position_dodge(width = .5)) 
```


```{r, eval = FALSE}
library(ggdist)
library(broom)
library(dplyr)
library(tidyr)
library(ggdist)
library(ggplot2)
library(broom)
library(modelr)
library(distributional)

m %>% 
 tidy() %>%
  ggplot(aes(y = term)) +
  stat_halfeye(
    aes(xdist = dist_student_t(df = df.residual(m), mu = estimate, sigma = std.error))
  )
```
